A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-05-12 paper/paper-jsdse/paper-jsdse.tex
Rewrite last paragraph in section 4.

Lastly, the race variable is almost perfectly matched. The \texttt{id}'s in the dropouts subset of the refreshed data all correspond to males, which perfectly matches the original subset.

>>>>

Lastly, the individuals in the dropouts subset of the refreshed data (as matched by their \texttt{id}s) belong to the same race as the individuals in the original data. This is also the case in the \texttt{sex} variables, which all correspond to males.

### 2022-05-12 paper/paper.Rmd
Rewrite last paragraph in section 4.

Lastly, the race variable is almost perfectly matched. The `id`'s in the dropouts subset of the refreshed data all correspond to males, which perfectly matches the original subset.

>>>>

Lastly, the individuals in the dropouts subset of the refreshed data (as matched by their `id`s) belong to the same race as the individuals in the original data. This is also the case in the `sex` variables, which all correspond to males.
